\subsection{Bennett}

\subsubsection*{Overview}
His greatest strength right now is his utility use. Bennett consistently finds ways to use smokes and
molotovs to pressure the enemy team and he doesn't seem afraid to experiment with smokes. He has a very
difficult time when confronting enemy players in straight-up duel situations, but doesn't usually have
trouble confirming kills that he is advantaged in. All that said he is definitely still developing his
playstyle so I will eagerly watch to see how he improves.

\subsubsection*{Strengths}
Utility, holding angles

\subsubsection*{Weaknesses}
aim, awareness

\subsubsection*{Recommended Positons}
support, entry fragger

\subsubsection*{Extra Notes}
Bennett has a few things to improve on and I think he will become a solid player. He's definitely still
developing his playstyle at the moment so I will only make a couple notes that may help him improve
more quickly.

\begin{itemize}
    \item In Genereal, he does a couple things wrong when fighting. The first is his ADADAD pattern. He clearly
    understands the idea: Strafe and counter-strafe to switch direction and fire a bullet when you're stopped,
    but his timing off, so he's usually moving when he fires. The second thing is that he doesn't flick to a target.
    (see: aim guide)

    \item I think in general Bennett plays really passive T side. His weaker aim probably
    leads him to avoid duels and engagements that may be necessary to execute agressive T
    side attacks. (see: trading)

    \item I think he should prioritize putting himself in situations where he can push aggressively
    with a teammate to ensure a trade.
\end{itemize}

\subsubsection*{Demo Review Notes}
\input{bennett-game1.tex}
