\subsection{JT}

\subsubsection{Overview}
	Very consistent with scoped weapons. While strong at holding angles with most weapons, JT
	is weak with rifles when compared to his overall preformance. His primary weaknesses appear
	to be rifling at mid and long ranges, and clearing angles while on rotate. He is often killed or forced into
	a scramble situation due to his neglegance when rotating around areas of the map he has little or
	no information about. Despite this weakness he is able to clinch many kills in disadvantaged situations
	due to his superior overall flicking ability and situational awareness
\subsubsection{Strengths}
	Scoped accuracy/flicks, Holding angles, Even duels, HE grenades, map awareness
\subsubsection{Weaknesses}
	Rifle accuracy, Crosshair placement, clearing angles, decisiveness
\subsubsection{Recommended Positons}
	AWPer, late round carry
\subsubsection{Extra Notes}
	JT has a couple of habits that are noteworthy here.

	He likes to take risks by challenging enemy players to duels that he is even or slightly disadvantaged
	in. His willingness to do so is likely influenced by his good flicking ability.

	JT has a tendancy to go for ninja defuses. While not necessarily a bad idea, he should be aware of
	situations where it may be beneficial to attempt to win by taking duels at isolated angles instead.

	Occasionally JT finds himself in a position where he must make a choice on limited information
	In these situations he often does not make a decision quickly, and instead will try to play some
	sort of middle ground between his options while he waits for more info. In these siuations he
	should probably aim to make a decision and rotate quickly, since waiting for more info almost always
	results in him having to play a retake situation.

\subsubsection{Demo Review Notes}
\input{jt-game1.tex}
