\documentclass{article}

\title{CS:GO Notes}
\date{}

\begin{document}
\maketitle

\section*{Preface}

	This document describes my basic understanding of how to play the game. This includes information
	such as what options are strongest in certain situations (eg. enemy AWP watching a long sightline).
	This was inspired by an idea I had to treat my teammates as RPG characters to 'deploy' them
	in situations where their strong points are advantaged. The second half of this document deescribes
	my observations of the strengths and weaknesses of each member of our team.

\section*{AIM FOR DUMMIES}

One thing I find generally helpful to keep in mind when aiming is to literally take my time with my shots. This has a couple
meanings, but most importantly it means that before I ever consider firing a bullet, I am going to confirm that my cursor is
all the way over to where I want it to be and that i'm not moving before I fire. Generally, the faster you can confirm that
your crosshair is correctly placed, the faster you can fire. So the whole motion takes the time of aiming and confirming your
target. Keep in mind that it feels like aiming takes a long time, and not to get hasty. It takes longer to aim an accurate shot
than it does to aim an inaccurate one. This means that you'll actually spend less time fighting overall however, since you will
be hitting more shots and killing your opponent more efficiently. When done quickly these look like flicks. Flicks are slightly
different in how they function, however, and I won't be covering them here yet as I don't think any description of flicking
I could provide right now would be beneficial.

\section*{Guidelines. Strategies, and Gameplay Techniques}

\subsection*{Trading}
Generally when attempting to make an aggressive play where clearing angles individually is not preferable or possible, players
will push in a team of 2 or more. The idea behind these pushes is to use your man advantage to increase the amount of time you
have to locate and kill an enemy. The reason it's so effective is because, when done properly, it near guarantees at least a
1 for 1 trade of players. Being able to force trades like this is important to keeping control of the pace of the match.

\subsection*{Holding Angles}
\begin{itemize}
    \item Generally, static holding angles is bad unless you've got a scope, improving your lethality at range due to better accuracy.

    \item Generally, if you're confident at range with your weapon you can static hold angles more effectively, but the real reason is
    peaker's advantage.

    \item If you're static holding an angle and your opponent peaks you, they have the advantage. But if you peek-unpeak an angle, you
    have a chance to peak after your opponent has pushed out, giving you peaker's advantage.
\end{itemize}

\subsection*{Taking Space}
One thing I often see go overlooked is the concept of space. Taking space on a map means controlling where your opponents can and
cannot be at any given time. Leveraging this concept well is fundamental to executing proper CT side holds and, especially, T side
attacks, and is the primary reason many players have trouble transitioning between T and CT sides. 
\begin{itemize}
    \item At the start of a normal bomb plant game Ts are attacking and CTs are defending.
    \item This means that CTs are trying to \textbf{Hold Space} and Ts are trying to \textbf{Take Space}
    \item To this end, many players quickly realize that Smokes and Molotovs are essential to controlling space due to their ability
    to directly deny enemy sight lines and ground space, respectively.
\end{itemize}
    One of the most effective ways to take space in a semi-coordinated setting is to \textbf{Entry Frag} on the location
    you want to take space in. This accomplishes one immediately obvious thing: getting a friendly player in the space you want to
    take. This effectively makes the space a no-mans-land for both teams until one side can confirm there are no enemy players in
    the space anymore. Even if your entry fragger doesn't get the kill, he opens the space up for the rest of his team to push behind
    him during the time he's running out. These few seconds are the most critical to a successful entry frag. Generally, entry fraggers
    work in pairs or with a coordinated team to confirm a trade of players. In most situations the attacking team should have the
    man-advantage when attempting to take an area, since the area that needs to be defended (eg. A and B sites) is much larger than
    the area that needs to be attacked (eg. A \textbf{or} B sites)

\subsection*{Solo Carrying}
There are many skills associated with playing in an uncoordinated setting that are worth examining. People often refer to this
type of playstyle as "solo carrying" due to it's effectiveness at making an impact on rounds to such an extent that the player
who masters these skills appears much more competant than those who focus only on playing in a team. Primary characteristics
of this playstyle include, but are not required or limited to:
\begin{itemize}
    \item utility setups for solo attacking/defending (eg. solo banana as T on inferno)
    \item good risk/reward management / decision making (high-risk high-reward, play making)
    \item good information collection and game awareness (aggressive CT side, counter-strats, quick rotates)
    \item high mechanical skill (aim, flicking, reaction time)
    \item high self-awareness to recongnize when the enemy team is adapting and changing plans
    \item a tilt-proof mindset
\end{itemize}
Probably the most important thing an aspiring solo carry player can aim for is to maximize their solo impact on a game. This means
that they're focusing on value they can guarantee during every game (eg. utility setups) and pushing the game in such a way that
they are able to control the pace of the match (risk-reward management). You can imagine a player who, on T side inferno,
pushes up banana with smokes and mollys, and gets a kill and takes banana control every round. Pratically, if you're succeeding
in getting map control and maybe a pick more than half of the time, you're making a good play and you're probably carrying the game
even if you aren't ace-ing rounds. A really good solo-carry player will be able to snowball a man-advantaged round into a win by
leveraging the other basic CS:GO skills like trading out teammates. This can quickly turn a 4v5 into a 1v2 and sometimes you'll
be able to net extra kills to really lock-down your man-advantage and win rounds handily.

As a final note, the most important thing to do in any game of CS:GO is to remain untilted. Sometimes, your team is throwing harder
than you can carry, and sometimes you just aren't good enough to carry against a well-equipped team. There are risks associated with
playing a solo-carry playstyle and coordinated teams will be able to exploit your high-risk decisions in a way that uncoordinated
teams just aren't equipped to. In these situations it's best to fall back on the CS fundamentals and use your judgement to make
decisions about how best to play against your opponents.

\section*{Teammate Observations}

	This section describes my observations of my teammates decision making during a match. This data is collected
	by re-watching the matches we play as a group and noting each decision the player makes, as well as the outcome
	of that decision. The goal is to establish a clear picture of each player's strengths and weaknesses to both
	identify points that should be worked on for improvement and to understand what situations each member of the
	team is strong in so we can have them in those positions as often as possible.

\include{JT}
\include{Jonathan}
\include{Jared}
\include{Bennett}
\include{Carson}

\end{document}
